Nonlinear Dendritic Coincidence Detection for Supervised Learning

### 2021-05-05 notes/draft_article.tex
.

\usepackage[numbers]{natbib}
\bibliographystyle{abbrvnat}

@@

		In a supervised learning scheme, where the top down input
		arriving at the apical compartment acts as the teaching signal,
		the most straight-forward learning rule for the basal synaptic
		weights would be derived from an appropriate loss function,
		such as a mean square error, based on the difference between 
		basal and apical input, i.e.\ $I_{\rm p} - I_{\rm d}$. Theoretical work has 
		investigated possible learning mechanisms
		that could utilize an intracellular error signal
		\citep{Urbanczik_2014,Schiess_2016,Guerguiev_2017}.
		However, a clear experimental
		evidence for a physical quantity encoding such an error 
		is---to our knowledge---yet to be found. 
		On the other hand, Hebbian-type plasticity is extensively
		documented in experiments. Therefore, our work is
		based on the question whether the non-linear interactions
		between basal and apical synaptic input could, when
		combined with a Hebbian plasticity rule, allow a neuron
		to learn to reproduce an apical teaching signal in its
		proximal input.

@@

		To be continued

>>>>

\usepackage[numbers]{natbib}
\bibliographystyle{nourlplainnat.bst}

@@

		In a supervised learning scheme, where the top down input
		arriving at the apical compartment acts as the teaching signal,
		the most straight-forward learning rule for the basal synaptic
		weights would be derived from an appropriate loss function,
		such as a mean square error, based on the difference between 
		basal and apical input, i.e.\ $I_{\rm p} - I_{\rm d}$. Theoretical work has 
		investigated possible learning mechanisms
		that could utilize an intracellular error signal
		\citep{Urbanczik2014,Schiess2016,Guerguiev2017}.
		However, a clear experimental
		evidence for a physical quantity encoding such an error 
		is---to our knowledge---yet to be found. 
		On the other hand, Hebbian-type plasticity is extensively
		documented in experiments \cite{Gustafsson1987,Debanne1994,Markram1997,Bi1998}. 
		Therefore, our work is
		based on the question whether the non-linear interactions
		between basal and apical synaptic input could, when
		combined with a Hebbian plasticity rule, allow a neuron
		to learn to reproduce an apical teaching signal in its
		proximal input.

@@

		The idea of target-backpropagation in multi-layered networks
		has already been proposed in different variants
		\cite{Bengio2014,Lee2015,Guerguiev2017}. Yet, all of these approaches
		assume a learning rule being dependent on an explicit error term 
		between top-down and bottom up signals guiding plasticity in some form
		or another.
